Estimating Neighborhood Rents with Scraped Data

### 2018-06-04 dashboard/index.rmd
progress on data section

---
title: "smooth-sea"
output: 
  flexdashboard::flex_dashboard:
    navbar:
       - {title: "hesscl.com", href: "http://hesscl.com", align: right}
       - {title: "Project Home", href: "http://hesscl.com/smooth-sea/index.html", align: left} 
    orientation: columns
    theme: bootstrap
    logo: "../logo.svg"
---

>>>>

---
title: "smooth-sea"
output: 
  flexdashboard::flex_dashboard:
    navbar:
       - {title: "Project Home", href: "../index.html", align: right} 
    orientation: columns
    theme: bootstrap 
    source: "https://github.com/hesscl/smooth-sea/dashboard"
---

### 2018-06-04 index.rmd
progress on data section

---
title: "Estimating Neighborhood Rents with Scraped Data"
output: 
  html_document:
      includes:
        in_header: header.html
        after_body: footer.html
---

@@

@@

[Working paper on estimating Seattle neighborhood rent indicators](./manuscript/index.html)

[`flexdashboard` for working paper's model diagnostics and forecasts](./dashboard/index.html)

[GitHub Repository](https://github.com/hesscl/smooth-sea/)

@@

### See also

@@

@@

Email Chris Hess at [hesscl@uw.edu](mailto://hesscl@uw.edu) for more information about this research.

>>>>

---
title: "Estimating Neighborhood Rents with Scraped Data"
output: 
  html_document:
      includes:
        in_header: "header.html"
        after_body: "footer.html"
---

@@

### About

The goal of this research is to understand the dynamics of Seattle neighborhoods' median rent level using scraped rental housing listings from Craigslist. I use a series of data visualizations to describe the accumulated data and compare the Craigslist estimates against other indicators. After the data description, I model a panel of quarterly census tract estimates to explain the spatial and temporal dynamics observed so far. Models are trained on quarterly tract estimates observed through the prior quarter and forecast the current quarter's rent surface.

@@

[Working paper](./manuscript/index.html) on estimating Seattle neighborhood rent indicators

[Results dashboard](./dashboard/index.html) for working paper's model diagnostics and forecasts

[GitHub Repository](https://github.com/hesscl/smooth-sea/) with source code for manuscript and results dashboard

@@

### Powered By

@@

[R Markdown](https://rmarkdown.rstudio.com) - Reproducible data analysis and manuscript creation

[flexdashboard](https://rmarkdown.rstudio.com/flexdashboard/index.html) - Easy interactive dashboards for R

[plot.ly](https://plot.ly/) - translate ggplot() objects to JavaScript-based htmlwidgets

[GitHub Pages](https://pages.github.com/) - Publish static web pages with repositories

@@

Email the project team at [searent@uw.edu](mailto://searent@uw.edu) for more information about this research.

### 2018-06-04 manuscript/index.Rmd
typo in index, reducing footer whitespace
progress on data section

---
title: "Estimating Neighborhood Rents with Scraped Data"
author: "Chris Hess"
date: "June 2, 2018"
output: 
  html_document:
    toc: true
    toc_float: true
    includes:
      in_header: header.html
      after_body: footer.html
abstract: "Online classified ads are a key source of information about local rental housing markets. This research asks what temporal and spatial dynamics explain neighborhood variations in one-bedroom rents in Seattle, WA, and contributes a novel approach to forecasting quarterly neighborhood rent levels using Bayesian models estimated with integrated nested Laplace approximations (INLA). All models were trained on data for 2017 Q2 through 2018 Q1, with forecasts for 2018 Q2 compared against the observed-to-date data for the current quarter (i.e. 2018 Q2). The top model assumes that spatial and temporal dynamics are separable, i.e. independent of each other, and non-interactive. This spatial random-effects model with AR(1) temporal structure achieves a mean absolute error (MAE) of about $90 for the training data and $145 for the test data."
---

@@

#load ACS data extract (codebook in folder)
census <- read_csv(file = "../input/acsExtract.csv")
censusRent <- read_csv(file = "../input/acsRent.csv")
census <- inner_join(census, censusRent)

@@

@@

@@

### Web scraping with Helena

>>>>

---
title: "Estimating Neighborhood Rents with Scraped Data"
author: "Chris Hess"
date: "June 2, 2018"
output: 
  html_document:
    toc: true
    toc_float: true
    includes:
      in_header: "header.html"
      after_body: "../footer.html"
abstract: "Online classified ads are a key source of information about local rental housing markets. This research asks what temporal and spatial dynamics explain neighborhood variations in one-bedroom rents in Seattle, WA, and contributes a novel approach to forecasting quarterly neighborhood rent levels using Bayesian models estimated with integrated nested Laplace approximations (INLA). All models were trained on data for 2017 Q2 through 2018 Q1, with forecasts for 2018 Q2 compared against the observed-to-date data for the current quarter (i.e. 2018 Q2). The top model assumes that spatial and temporal dynamics are separable, i.e. independent of each other, and non-interactive. This spatial random-effects model with AR(1) temporal structure achieves a mean absolute error (MAE) of about $90 for the training data and $145 for the test data."
---

@@

#load ACS data extract (codebook in folder)
census <- read_csv(file = "../input/acsExtract.csv")
censusRent <- read_csv(file = "../input/acsRent.csv")
census <- inner_join(census, censusRent) #1:1

@@

## Introduction

@@

### Web scraping using Helena

[Helena](http://helena-lang.org) is a high-level programming language for end users to automate web scraping as a method of data collection. Users write programs in an extension for Google Chrome by demonstrating the first row of data they want to collect using clicks, form interactions and highlighting values. The extension translates an initial demonstration into a starting script written in Helena, which a user can further modify or set to run on a regular schedule. Though Helena programs collect data roughly at the speed they are recorded at, users can run multiple programs in parallel to increase the volume of data collected. Data are stored on an AWS server where users can later query either the full table of scraped data or a subset scraped within a specified number of hours.

Helena learns where features of are through the user interface (UI) rather than the underlying document object model (DOM). Though the HTML code of a site may regularly change over the course of regular data scraping, websites less frequently undergo drastic overhauls to what their users interact with. Helena also uses skip blocks to avoid re-scraping the an already-collected item. These two aspects of Helena provide its programs robustness to common headaches encountered with web scraping by default. Overall, Helena's programming-by-demonstration method reduces time needed building a scraper from scratch, giving social scientists the capacity to quickly scrape a single table of data or build ongoing data processes.

For the UW team's data collection, a Helena program runs 24-hours a day and scrapes listings from the Seattle Craigslist. It is important to note that web scraping does violate Craigslist's Terms of Service, and that we are using all scraped data exclusively for academic research. For a more thorough discussion of this issue, consult page 3 of [Boeing and Waddell (2016)](https://arxiv.org/ftp/arxiv/papers/1605/1605.05397.pdf).

The key steps of any data process can be distilled into three tasks: a.) _extract_ a table of interest from a specified origin source, b.) _transform_ it to support the desire analyses and c.) _load_ the transformed data to a storage destination for future use. In the present case, a program extracts scraped listings observed since the database 
<br>

@@
